HPC--101\\Onboarding

### 2017-02-04 hpc_101/sections/02_cluster.tex
removed valuestorage and commented out stainability and related services
redo of history

\subsection{{\craycs}}
\begin{frame}
\frametitle{{\craycs} -- History}
\begin{itemize}
 \item Initial investment of 1.8 Million by the University of {\hawaii} (UH)
 \item Delivered in October of 2014
 \item Accepted in December of 2014 
 \item Early adopter testing started in January 2015
 \item Opened for general use in April 2015
 \item March 2016, 92 new nodes added to cluster, raising total core count from 3,800 to 5,876 cores
 \item January 2017, 5 new nodes added to cluster, raising total core count from 5,876 to 5,992 cores
 \item As of Nov 2016, more than 300 users have been granted access to the cluster
\end{itemize}
\end{frame}

>>>>

\subsection{{\craycs}}
\begin{frame}
\frametitle{{\craycs} -- History}
\begin{itemize}
\item[] 2014
  \begin{itemize}
  \item Jul. -- University of {\hawaii} (UH) selects Cray's proposal
  \item Oct. -- Delivered 184 nodes, 3,800 cores
  \item Dec. -- Passed testing and accepted
  \end{itemize}

\item[] 2015
  \begin{itemize}
  \item Jan. -- Early adopter testing started (8 users)
  \item Apr. -- Opened for general use
  \end{itemize}
\item[] 2016
  \begin{itemize}
  \item Mar. -- 92 nodes added, 5,876 cores total
  \end{itemize}
\item[] 2017
  \begin{itemize}
  \item Jan. -- 5 nodes added, 5,992 cores total
  \item Jan. -- 370$+$ users have been granted access to the cluster
  \end{itemize}
\end{itemize}
\end{frame}
